---
title: "Intro to R Markdown / GitHub Lecture"
author: "Lauren Littig"
output: github_document
---

I'm an R Markdown document! 

# Section 0: libraries and notes

* echo = F hides code chunks
* message = F hides addnl messages/suggestions
* eval = F makes code chunk not run
* TOC gives table of contents

```{r load_libraries}
library(tidyverse)
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100) # this samples from a normal distribution
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble

This plot shows the distribution of the absolute value of $X$

```{r echo = F, message = F}
set.seed(1)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)

ggplot(plot_df, aes(x = x)) + geom_histogram()

head(plot_df)
```
# Section 5: Learning Assessment 2

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?


```{r}
la_df = tibble(
  num_var = rnorm(n = 500, mean = 1),
  log_var = num_var > 0,
  abs_var = abs(num_var))

ggplot(la_df, aes(x = abs_var)) + geom_histogram()
```
The median is `r round(median(la_df$abs_var), 2)`

The median is `r round(median(pull(la_df, abs_var)), 2)`

Second way is preferable for reasons I dont get. Something about changing the dataset. 

# Section 6: Formatting

Text formatting
_____________________

*italic* or _italic_
**bold** or __bold__
`num_var`
superscript^2 and subscript~2~

Headings
_____________________

# 1st Level Header

## 2nd Level Header

### 3rd Level Header

Lists
---------------------
* Bulleted 
* Item 1a

1. Numbered list item 1
1. Item 2. Apparantly this wil be #2 when knitting (shows 1 in RStudio)


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: Learning Assessment 3
After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* The mean is `r mean(pull(la_df, num_var))`
* The median is `r median(pull(la_df, num_var))`
* The SD is `r sd(pull(la_df, num_var))`





